# Other tabling functions

## Other tabling functions

![](images/gtreg_overview_other.svg)

## tbl_reg_summary()

Create summary tables with standard regulatory formatting.

::: panel-tabset
### Code

```{r}
#| echo: true
#| eval: false
 df_patient_characteristics |> 
  tbl_reg_summary(
    by = trt, 
    include = c(marker, status)
    ) |> 
  bold_labels()
```

### Table

```{r}
#| echo: false
#| eval: true
 df_patient_characteristics |> 
  tbl_reg_summary(
    by = trt, 
    include = c(marker, status)
    )|> 
  bold_labels()
```

### Data

` df_patient_characteristics`

```{r}
#| echo: false
df_patient_characteristics |> 
  select(patient_id, trt, marker, status) |> 
  slice(1:5) |> 
  gt::gt() 
```
:::


## Exercise 3

<br>

**Recommended:** Enter the dedicated RStudio Cloud work space (with packages pre-installed) to complete Exercise 1. It may still be helpful to peek at the [exercises web page](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"} to verify that your tables match the desired output.

[Click here to enter R in Pharma RStudio Cloud work space for {gtreg}](https://rstudio.cloud/spaces/299322/join?access_code=Vnp96stsVIDLiEJI7AtHAQ4GB1gsptQgnOGb99_N){target="_blank"}

<br>

**Otherwise:** Use your personal computer and follow along the [exercises on the
website](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"}. Challenge yourself not to peek at the code solutions until you have completed the exercise.


```{r}
#| echo: false
#| cache: false
countdown(minutes = 10, font_size = "1.5em")
```


## tbl_listing()

A fancy 💅 way to print grouped data.

::: panel-tabset

### Code

```{r}
#| echo: true
#| eval: false
#| code-line-numbers: "5-7"
df_adverse_events |> 
  head(n = 10) |> 
  select(system_organ_class, adverse_event, grade, drug_attribution, patient_id) |> 
  arrange(adverse_event, desc(grade)) |> 
  tbl_listing(
    group_by = system_organ_class
    ) |> 
  bold_labels()
```

### Table

```{r}
#| echo: false
#| eval: true
df_adverse_events |> 
  head(n = 10) |> 
  select(system_organ_class, adverse_event, grade, drug_attribution, patient_id) |> 
  arrange(adverse_event, desc(grade)) |> 
  tbl_listing(
    group_by = system_organ_class
    ) |> 
  bold_labels()
```

### Data

`df_adverse_events`

```{r}
#| echo: false
df_adverse_events |> 
  head(n = 10) |> 
  select(system_organ_class, adverse_event, grade, drug_attribution, patient_id) |> 
  arrange(adverse_event, desc(grade)) |> 
  gt::gt()
```

:::

## tbl_listing() extensions

Remember this table?

```{r}
#| echo: false
#| eval: true
dat <- df_adverse_events |> 
  select(patient_id, system_organ_class, adverse_event, grade) |> 
  mutate(ae_label = case_when(
    adverse_event == "Anaemia" ~ "Term 1",
    adverse_event == "Increased tendency to bruise" ~ "Term 2",
    adverse_event == "Thrombocytopenia" ~ "Term 3"
  )) |> 
  slice(1:5)
```


::: panel-tabset

### Table

```{r}
#| echo: false
#| eval: true
dat |>
  tbl_listing(
    group_by = ae_label
  ) |> 
  bold_labels() |> 
  as_gt() |> 
  gt::tab_style(
    style = list(
      cell_fill(color = "#FFFBC8")
      ),
    locations = cells_body(rows = c(2, 4, 8))
  )
```

### Code

```{r}
#| echo: true
#| eval: false
#| code-line-numbers: "6-7"
dat |>
  tbl_listing(
    group_by = ae_label
  ) |> 
  bold_labels() |> 
  as_gt() |> 
  gt::tab_style(
    style = list(
      cell_fill(color = "#FFFBC8")
      ),
    locations = cells_body(rows = c(2, 4, 8))
  )
```

### Data

```{r}
#| echo: false
#| eval: true
dat |>
  gt::gt() 
```

:::


## Exercise 4

<br>

**Recommended:** Enter the dedicated RStudio Cloud work space (with packages pre-installed) to complete Exercise 1. It may still be helpful to peek at the [exercises web page](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"} to verify that your tables match the desired output.

[Click here to enter R in Pharma RStudio Cloud work space for {gtreg}](https://rstudio.cloud/spaces/299322/join?access_code=Vnp96stsVIDLiEJI7AtHAQ4GB1gsptQgnOGb99_N){target="_blank"}

<br>

**Otherwise:** Use your personal computer and follow along the [exercises on the
website](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"}. Challenge yourself not to peek at the code solutions until you have completed the exercise.


```{r}
#| echo: false
#| cache: false
countdown(minutes = 10, font_size = "1.5em")
```
