# Table shells

## Table shells

![](images/gtreg_overview_shell.svg)

## Strategy

<https://shannonpileggi.github.io/gtreg/articles/table-shells.html>

Table shells can be generated for any `tbl_ae()` and `tbl_reg_summary()` by:

1. Create dummy data or use your own data.

2. Pass the data to your function of choice.

3. Overwrite the statistic(s) shown to a fixed character string by implementing the
`style_xxx()` function in the `digits` argument.

. . . 

```{r}
style_xxx(8:11)
style_xxx(8:11, width = 4, digits = 1)
```


## Uniform shell for tbl_ae()

::: panel-tabset

### Code

```{r}
#| label: tbl_ae_modify_header_shell
#| echo: true
#| eval: false
#| code-line-numbers: "9,10,14"
df_adverse_events |> 
  tbl_ae(
    id = patient_id,
    id_df = df_patient_characteristics,
    strata = trt,
    ae = adverse_event,
    soc = system_organ_class, 
    by = grade, 
    digits = style_xxx,
    zero_symbol = NULL
  ) |> 
 bold_labels() |> 
 modify_header(all_ae_cols() ~ "**Grade {by}**") %>%
 modify_spanning_header(all_ae_cols(TRUE, TRUE) ~ "**{strata}**  \nN = xx")
```

### Table

```{r}
#| echo: false
#| eval: true
<<tbl_ae_modify_header_shell>>
```

### Data

::: columns
::: {.column width="65%"}
`df_adverse_events`

```{r}
#| echo: false
df_adverse_events |> 
  select(patient_id, trt, adverse_event, system_organ_class, grade) |> 
  slice(1:5) |> 
  gt::gt()
```
:::

::: {.column width="35%"}
`df_patient_characteristics`

```{r}
#| echo: false
df_patient_characteristics |> 
  select(patient_id, trt) |> 
  slice(1:5) |> 
  gt::gt() 
```
:::
:::
:::



## Custom shell for tbl_ae()

::: panel-tabset

### Code

```{r, tbl-ae-modify-header-shell-custom}
#| label: tbl_ae_modify_header_shell_custom
#| echo: true
#| eval: false
#| code-line-numbers: "9-13,17"
df_adverse_events |> 
  tbl_ae(
    id = patient_id,
    id_df = df_patient_characteristics,
    strata = trt,
    ae = adverse_event,
    soc = system_organ_class, 
    by = grade, 
    digits = list(
      style_xxx, # style for n
      function(x) style_xxx(x, width = 4, digits = 1) # style for %
    ),
    zero_symbol = NULL
  ) |> 
 bold_labels() |> 
 modify_header(all_ae_cols() ~ "**Grade {by}**") %>%
 modify_spanning_header(all_ae_cols(TRUE, TRUE) ~ "**{strata}**  \nN = xx")
```

### Table

```{r}
#| echo: false
#| eval: true
<<tbl_ae_modify_header_shell_custom>>
```

### Data

::: columns
::: {.column width="65%"}
`df_adverse_events`

```{r}
#| echo: false
df_adverse_events |> 
  select(patient_id, trt, adverse_event, system_organ_class, grade) |> 
  slice(1:5) |> 
  gt::gt()
```
:::

::: {.column width="35%"}
`df_patient_characteristics`

```{r}
#| echo: false
df_patient_characteristics |> 
  select(patient_id, trt) |> 
  slice(1:5) |> 
  gt::gt() 
```
:::
:::
:::


## Exercise 5

<br>

**Recommended:** Enter the dedicated RStudio Cloud work space (with packages pre-installed) to complete Exercise 1. It may still be helpful to peek at the [exercises web page](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"} to verify that your tables match the desired output.

[Click here to enter R in Pharma RStudio Cloud work space for {gtreg}](https://rstudio.cloud/spaces/299322/join?access_code=Vnp96stsVIDLiEJI7AtHAQ4GB1gsptQgnOGb99_N){target="_blank"}

<br>

**Otherwise:** Use your personal computer and follow along the [exercises on the
website](https://shannonpileggi.github.io/gtreg-workshop-rinpharma-2022/exercises.html){target="_blank"}. Challenge yourself not to peek at the code solutions until you have completed the exercise.


```{r}
#| echo: false
#| cache: false
countdown(minutes = 10, font_size = "1.5em")
```
